---
title: "cdx-summarize_analysis"
output: html_document
date: "2023-05-16"
editor_options: 
  chunk_output_type: console
---
New version of the script started 16.05.2023 to include the analysis and visualizations for the chapter (and to clean up previous versions).
Work in progress!

NB: Change chunk input to inline in order to include them in the report if knitted

# Knit to create pdf report
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r}
pacman::p_load(tidyverse,here,fs,ggplot2,reshape2,scales)
# here() makes it easy to access data and files in the project directory thereby avoiding 
# using pull paths
# fs is for file system stuff, e.g., dir_ls
# scales is used to show percentage on the y axis
```

# Set working directory
```{r}
setwd("/Users/au148767/Projects/warcnet-cdx-summarize-analysis/")
```

# Create read files function
A function for loading a set of cvs files into a dataframe while including (part of) the filename in a column (name "collection").
```{r}
read_data_files <- function(folder, glob_expression, col_names) {
  dir_ls(here(folder), glob = glob_expression) %>% 
    map_dfr(
      \(filename) {
        print(filename);
        read_csv(filename, col_names = col_names)  %>%
          add_column(
            collection = paste(str_split(basename(filename),"-",simplify = T)[1:2], collapse = "-")
          )
      }
    )
}
```

# 1. Total number of distinct domains from all countries and archives
Based on stata-distinct-domains-overall
```{r}
# read files with distinct domains overall (only one number)
distinct_domains_overall <- read_data_files("data", "*distinct-domains-overall.csv", c("n")) %>% 
  separate(collection, c("archive", "country"), remove=FALSE) # create columns with archive and country based on file name

# write to csv (optional)
# write_csv(distinct_domains_overall, "results/distinct_domains_overall.csv")
```

# 2. Number of distinct domains in all archives across years shown as facets
Based on stata-distinct-domains-per-year
TO DO: add nak data
TO DO: find a way to sort the facets so they appear in the correct order 
```{r}
# read files and remove years that are errors
clean_domains_per_year <- read_data_files("data","*domains-per-year.csv", c("year", "count")) %>%  
  filter(year > 1992)  %>%
  filter(year < 2022) %>% 
  separate(collection, c("archive", "country"), remove=FALSE)

# how many years are represented for each country in each archive? 
clean_domains_per_year %>% count(archive, country)

# collections as facets, full version
clean_domains_per_year |>
  ggplot(aes(x=year, y=count/1000000)) +
  geom_bar(stat="identity") +
  facet_wrap(~collection) +
  theme_minimal() +
  theme(legend.title=element_text(size = 16, face = "bold")) +
  theme(legend.text=element_text(size = 14, face = "bold")) + 
  theme(axis.text=element_text(size=14, face = "bold"),axis.title=element_text(size=14, face = "bold")) +
  theme(strip.text.x = element_text(size = 11, face = "bold"), strip.text.y = element_text(size = 11, face = "bold")) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = F)) +
  labs(y = "Number of domains in millions \n", x = "")

# collections as facets, only national archives
clean_domains_per_year  %>%
  filter(archive %in% c("bnf", "lwa", "szl")) %>% ### remember to include nak!
  ggplot(aes(x=year, y=count/1000000)) +
  geom_bar(stat="identity") +
  facet_wrap(~collection,ncol=2, labeller = labeller(collection = 
    c("bnf-all" = "BNF, all TLDs",
      "bnf-fr" = "BNF, only .fr",
      "lwa-all" = "LWA, all TLDs",
      "lwa-lu" = "LWA, only .lu",
      "szl-all" = "SZL, all TLDs",
      "szl-hu" = "SZL, only .hu"))) +
  theme_minimal() +
  scale_y_continuous(labels = function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = F)) +
  labs(y = "Number of domains in millions \n", x = "")

# collections as facets, only ccTLDs
clean_domains_per_year %>%
  filter(country!="all") %>%
  filter(country!="dk") %>% # as long as we don't have the Danish data, delete filter when we have the data
  mutate(across(collection, factor, levels=c("bnf-fr","lwa-lu","szl-hu", "ia-fr", "ia-lu", "ia-hu","cc-fr", "cc-lu", "cc-hu"))) %>%
  ggplot(aes(x=year, y=count/1000000)) +
  geom_bar(stat="identity") +
  facet_wrap(~collection,ncol=3) +
  theme_minimal() +
  scale_y_continuous(labels = function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = F)) +
  labs(y = "Number of domains in millions \n", x = "")
# TO DO: add labels
  
# for only one condition: filter(archive=="bnf") for only bnf OR filter(archive!="bnf") for all archives except bnf (!= means not equal to)
```

# 3. Each ccTLD across all archives - OLD VERSION
## .dk
Based on a file I have manually created called dk_all_archives, which is based on statc-distinct-lvl2-per-tld-per-year.
I have taken the .dk column from each of the files named statc-distinct-lvl2-per-tld-per-year, which means that 
dk_all_archives includes the number of second-level domains with the TLD .dk from each year that are in all the archives' holdings.
```{r}
dk_all_archives <- read_csv2("data/dk_all_archives.csv") 
# før hed den dk_all_archives <- read_csv2(here("data/dk_all_archives.csv")) men tror ikke here gør nogen forskel?
# dk_all_archives$year <- as.factor(dk_all_archives$year) # den gør vist ikke noget?

dk_all_archives_melt <- melt(dk_all_archives, 
                        id.var="year",
                        measure.vars = colnames(dk_all_archives)[! colnames(dk_all_archives) %in% c("year")],
                        variable.name = "archive", 
                        value.name = "n")

ggplot(data = dk_all_archives_melt, aes(x = year, y = n, group = archive, color = archive)) + 
  geom_point() + 
  geom_line(linewidth = 1.2) + 
  theme_minimal() +
  theme(legend.title=element_text(size = 16, face = "bold")) +
  theme(legend.text=element_text(size = 14, face = "bold")) + 
  theme(axis.text=element_text(size=14, face = "bold"),axis.title=element_text(size=16, face = "bold")) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = F)) +
  scale_color_brewer(palette="Spectral", labels = c("BNF","Common Crawl", "Internet Archive", "Luxembourg Web Archive", "Netarkivet", "Hungary Web Archive")) +
  labs(y = "Number of domains \n", x = "\n Year", color = "Archive") 

# alternative colours: scale_colour_manual(values = c("red", "blue", "gold", "green4", "darkviolet", "pink"), labels = c("BNF","Common Crawl", "Internet Archive", "Luxembourg Web Archive", "Netarkivet", "Hungary Web Archive")) + 
# so maybe select colours for the plot above and below that corresponds, i.e. the same for the same archive

# The numbers for Luxembourg and Hungary are so small that we can't really see them. If we want to see them, we could filter
dk_all_archives_lu_hu_bnf <- dk_all_archives_melt %>% 
  filter(archive == "lwa" | archive == "szl" | archive == "bnf")

ggplot(data = dk_all_archives_lu_hu_bnf, aes(x = year, y = n, group = archive, color = archive)) + 
  geom_point() + 
  geom_line(linewidth = 1.2) + 
  theme_minimal() +
  theme(legend.title=element_text(size = 16, face = "bold")) +
  theme(legend.text=element_text(size = 14, face = "bold")) + 
  theme(axis.text=element_text(size=14, face = "bold"),axis.title=element_text(size=16, face = "bold")) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = F)) +
  scale_colour_manual(values = c("gold", "darkviolet", "red"), labels = c("BNF","Luxembourg Web Archive", "Hungary Web Archive")) + 
  labs(y = "Number of domains \n", x = "\n Year", color = "Archive")
```

# 4. Top 15 TLDs in the different national archives
## Netarkivet
Based on statc-distinct-lvl2-per-tld-overall.
```{r}
# read data and add column names
dk_lvl2_per_tld <- read.csv("data/nak-dk-statc-distinct-lvl2-per-tld-overall.csv", header=FALSE) # It has no headers, so we add the column names
colnames(dk_lvl2_per_tld) = c("TLD","num_domains")

# to see the data to decide how many TLDs to include
head(dk_lvl2_per_tld, 20) # change the number depending on how many you want to see
  
# create top15 and an "Other" category with the rest
percentage_top15 <- dk_lvl2_per_tld %>% 
  arrange(desc(num_domains)) %>% # probably not necessary but just to make sure they are properly sorted
  split(c(rep("top", 15), rep("rest", nrow(.) - 15))) %>% # splits into the top 15 and the rest
  (\(s) bind_rows(s$top, data.frame(TLD = "Other", num_domains = sum(s$rest$num_domains)))) %>% # sums num_domains for all from the "other" category
  mutate(percentage = num_domains/sum(num_domains)) # creates a column with the percentages for each TLD and the Other category 

# plot with reorder to order descending based on percentage but with  
percentage_top15 %>% ggplot(aes(x=reorder(TLD, -percentage) %>% fct_relevel("Other", after = Inf), y=percentage)) + 
  geom_bar(stat="identity", fill="royalblue") +
  theme_minimal() +
  scale_y_continuous(labels = percent) +
  labs(y = "Percentage from different TLDs \n", x = "\n TLD")  

# -percentage means that the order is descending (based on num_domains)
# Inf er for infinite, so here it means that the Other category is placed at the end
# to plot it with Other where it is placed depending on descending num_domains, remove: %>% fct_relevel("Other", after = Inf)
```

### Alternative ways of plotting Top 15 TLDs in the different national archives
Based on percentage_top15 generated in the previous analysis
```{r}
# 1st alternative: plot as bars, reorder by row_id

# new dataframe, just a copy of the other
percentage_top15_alt <- percentage_top15

# create row_id matching the number of rows of the dataframe
row_id <- seq(1, nrow(percentage_top15_alt))

# add the vector to the dataframe using $ symbol.
percentage_top15_alt$row_id = as.factor(row_id)

# create a list with the TLDs to use as labels
tld_names <- percentage_top15_alt %>% pull(TLD) 
  # alternative: to have Other where it is placed based on num_domains percentage_top15 %>% arrange(desc(percentage)) %>% pull(TLD)

# plot
percentage_top15_alt %>% ggplot(aes(x=row_id, y=percentage)) + 
    geom_bar(stat="identity", fill="royalblue") +
    scale_x_discrete(labels=tld_names)

# 2. alternative: plot as a stacked column - ordered alphabetically
percentage_top15 %>% ggplot(aes(x=1, y=percentage, fill=TLD)) + 
    geom_bar(position="fill", stat="identity") +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  scale_y_continuous(labels = percent)
```

# 5. Overlap analysis
## .dk
Based on overlaps_hosts_dk that I have manually created based on the data in netarkivet-ccdk-iadk-overlap
###### TO DO: I have reordered the columns so they were in the opposite order of before - do so for the other csv's and remove _2 from the name 
OR can this be done with one of Ulrich's suggestions?
```{r}
# read data
overlaps_hosts_dk <- read_csv2("data/overlaps_hosts_dk_2.csv")

# create long format for ggplot
overlaps_hosts_dk_melt <- melt(overlaps_hosts_dk, 
                        id.var="Year",
                        measure.vars = colnames(overlaps_hosts_dk)[! colnames(overlaps_hosts_dk) %in% c("Year")],
                        variable.name = "Archive", 
                        value.name = "n")
# plot
overlaps_hosts_dk_melt %>% ggplot(aes(x=Year, y=n, fill=Archive)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  theme(legend.title=element_text(size = 16, face = "bold")) +
  theme(legend.text=element_text(size = 14, face = "bold")) + 
  theme(axis.text=element_text(size=14, face = "bold"),axis.title=element_text(size=16, face = "bold")) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = F)) +
  scale_x_continuous(breaks = clean_domains_per_year$year) +
  scale_fill_manual(values = c("cadetblue2","cornflowerblue","aquamarine","blue","cyan","dodgerblue","navyblue"),labels = c("Internet Archive","Common Crawl","Netarkivet","Internet Archive & Common Crawl","Netarkivet & Common Crawl","Netarkivet & Internet Archive","Netarkivet, Internet Archive & Common Crawl")) + 
  labs(y = "Number of .dk domains \n", x = "\n Year", color = "Archive")
```


###  QUESTION: Do we need to plot the statc-distinct-lvl2-per-tld-per-year as well? This would show the changes over time!
```{r}
# read data
dk_lvl2_per_tld_per_year <- read_csv("data/nak-dk-statc-distinct-lvl2-per-tld-per-year.csv")
```


# VERSION 2: Can I use lvl2 til at trække data ud til at lave df til "3. Each ccTLD across all archives"
```{r}
# read data using function
lvl2_per_tld_per_year <- read_data_files("data", "*distinct-lvl2-per-tld-per-year.csv", c("n")) %>% 
  separate(collection, c("archive", "country"), remove=FALSE) 

# rename the first instance in archive (row one, column 34) to year
lvl2_per_tld_per_year$archive[1] <- "year"

# nrow(lvl2_per_tld_per_year) # number of rows
# ncol(lvl2_per_tld_per_year) # number of columns

# create dataframe for a country and clean data
dk_across_archives <- lvl2_per_tld_per_year %>% subset(n == "dk" | archive == "year") %>% select(-c("n","collection","country")) %>% select(archive, everything())

#### could all this be done before subset, so you don't have to do it for each country?
dk_across_archives <- t(dk_across_archives) # transpose df
column_names <- dk_across_archives[1,] # create vector from row 1
colnames(dk_across_archives) <- column_names # use vector to assign column names
dk_across_archives <- dk_across_archives[-c(1,31,32),] # remove row 1, 31 and 32 (row with archive names + year 2022 og 2023)  
dk_across_archives <- data.frame(dk_across_archives)
dk_across_archives <- dk_across_archives %>% mutate(across(everything(), trimws)) # remove whitespace, don't know why that was introduced!
dk_across_archives <- dk_across_archives %>% mutate_at(c("bnf", "cc", "ia", "lwa", "nak", "szl"), as.numeric)
dk_across_archives$year <- as.factor(dk_across_archives$year)

# other versions
fr_across_archives <-  subset(lvl2_per_tld_per_year_clean, tld == "fr")
hu_across_archives <-  subset(lvl2_per_tld_per_year_clean, tld == "hu")
lu_across_archives <-  subset(lvl2_per_tld_per_year_clean, tld == "lu")
```


### FORSØG på at lave analyse 3 med den nyskabte dk_across_archives 
dk_all_archives includes the number of second-level domains with the TLD .dk from each year that are in all the archives' holdings.
```{r}
dk_across_archives_melt <- melt(dk_across_archives, 
                        id.var="year",
                        measure.vars = colnames(dk_across_archives)[! colnames(dk_across_archives) %in% c("year")],
                        variable.name = "archive", 
                        value.name = "n")
# change class
# dk_across_archives_melt$year <- as.factor(dk_across_archives_melt$year)
# dk_across_archives_melt$archive <- as.factor(dk_across_archives_melt$archive)
# dk_across_archives_melt$n <- as.numeric(dk_across_archives_melt$n)

# plot
ggplot(data = dk_across_archives_melt, aes(x = year, y = n, group = archive, color = archive)) + 
  geom_point() + 
  geom_line(linewidth = 1.2) + 
  theme_minimal() +
  theme(legend.title=element_text(size = 16, face = "bold")) +
  theme(legend.text=element_text(size = 14, face = "bold")) + 
  theme(axis.text=element_text(size=14, face = "bold"),axis.title=element_text(size=16, face = "bold")) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = F)) +
  scale_color_brewer(palette="Set1", labels = c("BNF","Common Crawl", "Internet Archive", "Luxembourg Web Archive", "Netarkivet", "Hungary Web Archive")) +
  labs(y = "Number of domains \n", x = "\n Year", color = "Archive") 

# alternative colours: scale_colour_manual(values = c("red", "blue", "gold", "green4", "darkviolet", "pink"), labels = c("BNF","Common Crawl", "Internet Archive", "Luxembourg Web Archive", "Netarkivet", "Hungary Web Archive")) + 
# so maybe select colours for the plot above and below that corresponds, i.e. the same for the same archive

# The numbers for Luxembourg and Hungary are so small that we can't really see them. If we want to see them, we could filter
dk_across_archives_lu_hu_bnf <- dk_across_archives_melt %>% 
  filter(archive == "lwa" | archive == "szl" | archive == "bnf")

ggplot(data = dk_across_archives_lu_hu_bnf, aes(x = year, y = n, group = archive, color = archive)) + 
  geom_point() + 
  geom_line(linewidth = 1.2) + 
  theme_minimal() +
  theme(legend.title=element_text(size = 16, face = "bold")) +
  theme(legend.text=element_text(size = 14, face = "bold")) + 
  theme(axis.text=element_text(size=14, face = "bold"),axis.title=element_text(size=16, face = "bold")) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = F)) +
  scale_colour_manual(values = c("gold", "darkviolet", "red"), labels = c("BNF","Luxembourg Web Archive", "Hungary Web Archive")) + 
  labs(y = "Number of domains \n", x = "\n Year", color = "Archive")
```


